The instability of variational quantum mechanics with Gaussian approximants is (not) entirely due to the unstable least squares problem

### 2013-06-12 paper.tex
Bracket code written
First integration script

In the first choice, the quantum state at time $t$ is expanded over a truncated Fock basis $|N〉$, as 
$$|ν(c(t))〉=|N〉c(t).$$
Schrödinger's equation expands to
$$|N〉Dc(t)=|D(ν\circ c)(t)〉≈{H\over i\hbar}|ν(c(t))〉≈|N〉〈N|{H\over i\hbar}|N〉c(t),$$
whence
$$Dc(t)≈〈N|{H\over i\hbar}|N〉c(t).$$
In this method, we set
$$vⁿ=cⁿ\qquad{\rm and}\qquad fⁿ=〈N|{H\over i\hbar}|N〉c(t),$$
solving Schrödinger's equation quite conventionally.

>>>>

In the first choice, the quantum state at time $t$ is expanded over a truncated Fock basis $|N〉$, as 
$$|ν(c(t))〉=|N〉c(t).$$
Schrödinger's equation expands to
$$|N〉Dc(t)=|D(ν\circ c)(t)〉≈{H\over i\hbar}|ν(c(t))〉≈|N〉〈N|{H\over i\hbar}|N〉c(t),$$
whence
$$Dc(t)≈〈N|{H\over i\hbar}|N〉c(t).$$
In this method, we set
$$vⁿ=cⁿ\qquad{\rm and}\qquad fⁿ=-i〈N|{H\over\hbar}|N〉c(t),$$
solving Schrödinger's equation quite conventionally.  Note that $|N〉$ diagonalises $H$, so this is especially simple.
